\documentclass[proceedings]{rmaa}

% a command to specify possible linebreak points in an email address
\newcommand{\D}{\discretionary{}{}{}}

\begin{document}
\begin{abstracts}[Abstract oral contribution]

  \title{Observational evidence of star formation stochasticity in the
  CALIFA dataset}

  \author{N. Romero-D\'iaz\altaffilmark{1}, J.E Forero-Romero\altaffilmark{1}}

        \altaffiltext{1}{Departamento de F\'isica, Universidad de los Andes,
          Cra 1 18A-10, Bloque Ip, Bogot\'{a}, Colombia. 
          (n.romero1661\D{}@uniandes.\D{}edu.\D{}co).}


  % List of authors used to construct table of contents
  \listofauthors{N. Romero-D\'iaz \& J.E. Forero-Romero}
  % Each author in Surname, Initials format, used in generating Author
  % Index entries.
  \indexauthor{Romero-D\'iaz, N.}
  \indexauthor{Forero-Romero, J.E.}

  \abstract{ It is generally accepted that a galaxy's total luminosity
    in the UV continuum and other emission line intensities are
    proportional to its Star Formation Rate (SFR). 
    However, there is theoretical evidence that for low SFR values
    stochastic effects in the star formation process can break this
    proportionality. 
    The stochasticity produces \emph{distributions} of UV luminosities
    and emission line intensities for a given SFR instead of the
    deterministic unique expected value.
    In this work we analyze data from the public data releases of
    the Calar Alto Legacy Integral Field Area (CALIFA) Survey 
    to test for the presence of these stochastic effects.
    We find some marginal evidence on the galaxy's outskirts for these
    stochastic events.
    We discuss the implications of our results for different
    theories of clustered star formation. 
    We also present possible observational strategies that might make
    this effect detectable with more significance in the near future.   
  }

\end{abstracts}
\end{document}
